The Name of the Title Is Hope

### 2024-05-22 paper/CCS/paper.tex
Paper draft

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Despite the recent growth of zero-knowledge succinct argument 
  of knowledge (ZKSNARK) in cryptocurrencies, 
  sigma protocol remains a popular choice in electronic voting to maintain privacy 
  and verifiability of elections and still used in prominent e-voting systems such as 
  Helios, Belenois, and SwissPost \textbf{More examples}. However, 
  the existing implementations of sigma protocol have two 
  shortcomings: (i) the same code is written twice, once for the front-end (JavaScript)
  and once for the back-end (Python/OCaml/Java), which is time-consuming but more importantly error-prone, 
  and (ii) none of these implementations offer any security guarantees. 
  In this paper, we present a certified implementation of sigma protocol in the Coq proof assistant. 
  We prove that our implementation is (special) sound, complete, and 
  (honest verifier) zero-knowledge. Moreover, 
  we compile our Coq formalisation to WebAssembly and Rust, and 
  thereby solve the problem of writing the same code twice. 
  We demonstrate the applicability of our
  formalisation by encoding the cryptographic protocols implemented in 
  Helios, Belenois, and SwissPost voting systems. 
  Our long terms goal is to provide a verified cryptographic library that can be 
  readily used in privacy-preserving voting systems.

@@

@@

Finally we establish the completeness, special soundness, 
and special honest-verifier zero-knowledge proof. 
\begin{lstlisting}[language=Coq]
Lemma schnorr_completeness : 
  forall (r c : F) (a : t G 1) (c r : t F 1),
  (a; c; r) = (schnorr_protocol x g r c) ->
  accepting_conversation g h (a; c; r) = true.
Proof. (* proof terms omitted *) Qed.

@@

@@

  \subsection{Parallel Composition}
  Explain the parallel composition of sigma protocols.

  \subsection{And Composition}
  Explain the and composition of sigma protocols.

  \subsection{Or Composition}
  Explain the or composition of sigma protocols.

  \subsection{Equality Composition}
  Explain the equality composition of sigma protocols.

  \subsection{Inequality Composition}
  Explain the inequality composition of sigma protocols.

@@

\section{DECRA}
The aim of this project is to investigate the applicability of 
zero-knowledge succinct argument of knowledge (ZKSNARK) 
to reduce the data breaches.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Despite the recent growth of zero-knowledge succinct argument 
  of knowledge (ZKSNARK) in cryptocurrencies, 
  sigma protocol remains a popular choice in electronic voting to maintain privacy 
  and verifiability of elections and still used in prominent e-voting systems such as 
  Helios, Belenois, and SwissPost. However, 
  the existing implementations of sigma protocol have two 
  shortcomings: (i) the same code is written twice, once for the front-end (JavaScript)
  and once for the back-end (Python/OCaml/Java), which is time-consuming but more importantly error-prone, 
  and (ii) none of these implementations offer any security guarantees. 
  In this paper, we present a certified implementation of sigma protocol in the Coq proof assistant. 
  We prove that our implementation is (special) sound, complete, and 
  (honest verifier) zero-knowledge. Moreover, 
  we compile our Coq formalisation to WebAssembly and Rust, and 
  thereby solve the problem of writing the same code twice. 
  We demonstrate the applicability of our
  formalisation by encoding the cryptographic protocols implemented in 
  Helios, Belenois, and SwissPost voting systems. 
  Our long terms goal is to provide a verified cryptographic library that can be 
  readily used in privacy-preserving voting systems.

@@

Electronic voting offers convenience and efficiency in an electoral process, 
potentially improving accessibility for disabled voters, increasing participation 
among overseas voters, and lowering the costs associated with conducting elections.
To ensure that electronic voting adheres to the principles of a (free and fair) 
paper-ballot election, we need two important ingredients: privacy and 
verifiability. We achieve privacy in a paper-ballot election by ensuring 
that no identifying present on a ballot to the voter, and verifiability 
is ensured by means of scrutineers. To have a similar effect in electronic 
voting, robust encryption techniques is employed to safeguard the privacy 
of voter choices, while audit trails (zero-knowledge proof)
allow voters and independent observers to verify the integrity 
of the voting process. But even the most 
sophisticated cryptographic techniques are useless if their software
implementation contains bugs. In fact, 
there is a history of bugs, varying from trivial to critical, 
in electronic voting software programs employed for democratic 
elections, e.g., Scytl/SwissPost \cite{9152765} (used in Swiss election), 
Voatz \cite{255334} (used in West Virginia, USA election),
Democracy Live Online Voting System \cite{263858} 
(used in Delaware, West Virginia, and New Jersey, USA election), 
Moscow Internet Voting System \cite{10.1007/978-3-030-51280-4_3}
(used in Russia election), iVote System \cite{10.1007/978-3-319-22270-7_3, 10.1145/3014812.3014837} 
(used in New South Wales, Australia election). 
Most of these software programs 
establish their correctness by means of testing, which 
does not capture all the possible scenarios. 
Interestingly, most of these bugs were found by researchers
who inspected the code after the source code was made public, 
even though the companies developing these proprietary software programs had 
claimed that they were bug free.

Two imporant ingredients for 
electronic voting are privacy and verifiability. While privacy 
ensures that no ... while verifiability ensures ....

Cryptographic techniques are used to achive privacy 
but even the most 
sophisticated cryptographic techniques are useless if their software
implementation contains bugs.

However, security 
experts often find the vulnerabilities in the deployed software that 
could undermine the integrity of an election (\textbf{cite all the work of 
software bug}).

Despite the concerns, many jurisdictions are already using 
electronic voting as a means to modernising their electoral process.

But even the most 
sophisticated cryptographic techniques are useless if their software
implementation contains bugs, and so evoting also requires
“software independence”

@@

Finally we establish the completeness, special soundness, 
and special honest-verifier zero-knowledge proof.

\begin{lstlisting}[language=Coq]
Lemma schnorr_completeness : 
  forall (r c : F) (a : t G 1) (c r : t F 1),
  (a; c; r) = (schnorr_protocol x g r c) ->
  accepting_conversation g h (a; c; r) = true.
Proof. (* proof terms omitted *) Qed.

@@

\begin{lstlisting}[language=Coq]

@@

@@
